Randomized trace estimation for parameter-dependent matrices applied to spectral density approximation

### 2024-09-23 paper/re-pro-badge.tex
automatically reproduce paper

The code for our numerical experiments can be found on \url{https://github.com/FMatti/Rand-TRACE}. The figures and tables were generated from the commit \href{https://github.com/FMatti/Rand-TRACE/tree/ab895e9}{ab895e9} on 2024-09-19 at 07:36:41 UTC.

>>>>

The code for our numerical experiments can be found on \url{https://github.com/FMatti/Rand-TRACE}. The figures and tables were generated from the commit \href{https://github.com/FMatti/Rand-TRACE/tree/7c053ed}{7c053ed} on 2024-09-23 at 17:06:23 UTC.
